Experience in Modeling a Microcontroller Instruction Set Using B

### 2012-05-15 trunk/papers/ArticleZ80/source/paper.tex
novos pequenos ajustes2

Two development strategies were important to improve the verification of 3062
proof obligations: the intensive use of parallelism and user pass. The Z80 module
was decomposed in 8 modules of instructions, it was very helpful to decrease the
time for verification. Because AtelierB can run simultaneously \textit{N} instances of 
provers, one per module, reducing the time verification by up to \textit{N}  times when
a processor with \textit{N} cores is used  or the process is submitted to \textit{N} 
networked computers. So we also set up a proving environment consisting of networked
computers to take advantage of the distribution facilities provided in the B development
environment.
% Resumo de como aconteceu o processo de verificação,
A second interesting strategy  was to reuse the user pass. Usually, an used
user pass to aid the verification of one proof obligation can solve several
similar proof obligations. Thus, few generic user pass are needed to prove many
proof obligations. As there are many similar assembly instructions, some
human-directed proofs, when replayed, could discharge other proof obligations. A
good example is a set of 17 user pass that quickly aided the verification of
approximately 2533 of WD proofs.

>>>>

Two development strategies were important to improve the verification of 3062
proof obligations: the intensive use of parallelism and user pass. The Z80 module
was decomposed in 8 modules of instructions, it was very helpful to decrease the
time for verification. Because AtelierB can run simultaneously \textit{N} instances of 
provers, one per module, reducing the time verification by up to \textit{N}  times when
a processor with \textit{N} cores is used  or the process is submitted to \textit{N} 
networked computers. So we also set up a proving environment consisting of networked
computers to take advantage of the distribution facilities provided in the B development
environment.
% Resumo de como aconteceu o processo de verificação,
A second interesting strategy  was to reuse the user pass. Usually, an used
user pass to aid the verification of one proof obligation can solve several
similar proof obligations. Thus, few generic user passes are needed to prove many
proof obligations. As there are many similar assembly instructions, some
human-directed proofs, when replayed, could discharge other proof obligations. A
good example is a set of 17 user passes that quickly aided the verification of
approximately 2533 of WD proofs.
